### 2015-06-13 improv.tex
Mostly streamlining the text in the alp section

Since most of our analysis in sections~\ref{sec:lubp} and ~\ref{sec:alubp} depended on showing that $\Gamma$ is a contraction map in the $L_\infty$ norm we first show that $\Gamma$ is also a contraction map in the weighted $L_\infty$ norm.
\begin{lemma}\label{gshiftmn}
Let $J_1\in \R^n$ and $k\in \R$ be a constant. If $J_2=J_1+k\psi$, then $\Gamma J_2\leq \Gamma J_1+\beta_{\psi} k\psi$.
\end{lemma}
\begin{proof}
The result follows in a similar manner as the proofs for Lemmas~\ref{gshift} and ~\ref{tgshift} by using the result in Lemma~\ref{lpsol}.
\end{proof}
\begin{theorem}\label{gmaxcontramn}
The operator $\Gamma  \colon \R^n\ra \R^n$ is a contraction operator in weighted $L_\infty$ with factor $\beta_{\psi}$.
\end{theorem}
\begin{proof}
Given $J_1,J_2\in \R^n$ let $\epsilon=||J_1-J_2||_{\infty,1/\psi}$. Thus
\begin{align}\label{ineq}
J_2-\epsilon\psi\leq J_1\leq J_2+\epsilon \psi.
\end{align}
From Lemmas~\ref{gmonotone} and ~\ref{gshiftmn}, we can write
\begin{align}\label{ineq}
\Gamma J_2-\beta_{\psi} \epsilon\psi\leq \Gamma J_1\leq \Gamma J_2+\beta_{\psi} \epsilon\psi.
\end{align}
Thus
\begin{align}
||\Gamma J_1-\Gamma J_2||_{\infty,1/\psi}\leq \beta_{\psi} ||J_1-J_2||_{\infty,1/\psi}.
\end{align}
\end{proof}
\begin{corollary}\label{hgmaxcontramn}
$\hg$ is also a contraction map in the weighted $L_\infty$ norm.
\end{corollary}
\begin{proof}
Follows from arguments similar to Theorem~\ref{gmaxcontramn}.
\end{proof}
\begin{lemma}\label{cmt1mn}
Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\eqdef\argmin_{r\in \R^k}||J^*-\Phi r||_{\infty,1/\psi}$ then
\begin{align}
||J^*-\hv||_{\infty,1/\psi}\leq \frac{2||J^*-\Phi r^*||_{\infty,1/\psi}+||\Gamma J^*-\hg J^*||_{\infty,1/\psi}}{1-\beta_{\psi}}.
\end{align}
\end{lemma}
\begin{proof}
The proof follows from Lemma~\ref{gmaxcontramn}, Corollary~\ref{hgmaxcontramn} and by replacing the $||\cdot||_\infty$ norm by $||\cdot||_{\infty,1/\psi}$ in the arguments presented in sections~\ref{sec:lubp} and ~\ref{sec:alubp} leading to Corollary~\ref{cmt1}.
\end{proof}\\
We now recall Lemma~$4.5$ of \cite{ALP}. \todoc{You had 4.3 here, but in the official journal version this seems to be Lemma 5 in Section 4.}
\begin{lemma}\label{restate}
Let $\psi$ be a Lyapunov function that belongs to the column span of $\Phi$ , $r \in \R^k$ be an arbitrary vector and let $r'$ be such that
\begin{align}
\Phi r'=\Phi r+||J^*-\Phi r||_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, \psi.
\end{align}
Then $r'$ is feasible for the ALP in \eqref{alp}. 
\end{lemma}
\begin{theorem}\label{mt2mn}
Let $\hv$ be the solution to the iterative scheme in \eqref{apvi} and let $\hj=\Phi \hr$ be the solution to the GRLP. Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_{\infty,1/\psi}$ be the error due to ALUB projection and let $r^*\eqdef\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_{\infty,1/\psi}$, then
\begin{align}
||\hj-\hv||_{1,c}&\leq \frac{c^\top \psi}{1-\beta_\psi}(4||J^*-\Phi r^*||_{\mn}
%\nn\\&
+||\Gamma J^*-\hg J^*||_{\mn}).
\end{align}
\end{theorem}
\begin{proof}
Let $\gamma=||J^*-\Phi r^*||_{\infty,1/\psi}$, then by choosing $r'$ as in Lemma~\ref{restate} we have
\begin{align}
||\Phi r'-J^*||_{\mn}&\leq ||\Phi r^*-J^*||_{\mn}+||\Phi r'-\Phi r^*||_{\mn}\nn\\
&=\gamma+\frac{1+\beta_\psi}{1-\beta_\psi}\gamma\nn\\
&=\frac{2}{1-\beta_\psi}\gamma.\nn
\end{align}
Since $r'$ is also feasible for the GRLP in \eqref{grlp} we have
\begin{align}
||\hj-\hv||_{1,c}&\leq||\Phi r'-\hv||_{1,c}\nn\\
&=\sum_{s\in S}c(s)\psi(s)\frac{|\Phi r'(s)-\hv(s)|}{\psi(s)}\nn\\
&\leq c^\top \psi ||\Phi r'-\hv||_{\infty,1/\psi}\nn\\
&\leq c^\top \psi (||\Phi r'-J^*||_{\infty,1/\psi}+||J^*-\hv||_{\infty,1/\psi}).
\end{align}
The result follows from Corollary~\ref{cmt1}.\\
\textbf{Main Result~$1$: Prediction Error bound in weighted $L_\infty$-norm}
\end{proof}
\begin{theorem}\label{cmt2mn}
Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2mn}, then
\begin{align}\label{finalbndmn}
||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(6 ||J^*-\Phi r^*||_{\mn}
%\nn\\&
+2||\Gamma J^*-\hg J^*||_{\mn}).
\end{align}
\end{theorem}
\begin{proof}
\begin{align}
||J^*-\hj||_{1,c}&\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn\\
&\leq c^\top \psi ||J^*-\hv||_{\mn}+||\hv-\hj||_{1,c}.\nn
\end{align}
The result now follows from Lemma~\ref{cmt1mn} and Theorem~\ref{mt2mn}.
\end{proof}\\

>>>>

Since most of our analysis in sections~\ref{sec:lubp} and ~\ref{sec:alubp} depended on showing that $\Gamma$ is a contraction map in the $L_\infty$ norm we first show that $\Gamma$ is also a contraction map in the weighted $L_\infty$ norm.
\begin{lemma}\label{gshiftmn}
Let $J_1\in \R^n$ and $k\in \R$ be a constant. If $J_2=J_1+k\psi$, then $\Gamma J_2\leq \Gamma J_1+\beta_{\psi} k\psi$.
\end{lemma}
\begin{proof}
The result follows in a similar manner as the proofs for Lemmas~\ref{gshift} and ~\ref{tgshift} by using the result in Lemma~\ref{lpsol}.
\end{proof}
\begin{theorem}\label{gmaxcontramn}
The operator $\Gamma  \colon \R^n\ra \R^n$ is a contraction operator in weighted $L_\infty$ with factor $\beta_{\psi}$.
\end{theorem}
\begin{proof}
Given $J_1,J_2\in \R^n$ let $\epsilon=||J_1-J_2||_{\infty,1/\psi}$. Thus
\begin{align}\label{ineq}
J_2-\epsilon\psi\leq J_1\leq J_2+\epsilon \psi.
\end{align}
From Lemmas~\ref{gmonotone} and ~\ref{gshiftmn}, we can write
\begin{align}\label{ineq}
\Gamma J_2-\beta_{\psi} \epsilon\psi\leq \Gamma J_1\leq \Gamma J_2+\beta_{\psi} \epsilon\psi.
\end{align}
Thus
\begin{align}
||\Gamma J_1-\Gamma J_2||_{\infty,1/\psi}\leq \beta_{\psi} ||J_1-J_2||_{\infty,1/\psi}.
\end{align}
\end{proof}
\begin{corollary}\label{hgmaxcontramn}
$\hg$ is also a contraction map in the weighted $L_\infty$ norm.
\end{corollary}
\begin{proof}
Follows from arguments similar to Theorem~\ref{gmaxcontramn}.
\end{proof}
\begin{lemma}\label{cmt1mn}
Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\eqdef\argmin_{r\in \R^k}||J^*-\Phi r||_{\infty,1/\psi}$ then
\begin{align}
||J^*-\hv||_{\infty,1/\psi}\leq \frac{2||J^*-\Phi r^*||_{\infty,1/\psi}+||\Gamma J^*-\hg J^*||_{\infty,1/\psi}}{1-\beta_{\psi}}.
\end{align}
\end{lemma}
\begin{proof}
The proof follows from Lemma~\ref{gmaxcontramn}, Corollary~\ref{hgmaxcontramn} and by replacing the $||\cdot||_\infty$ norm by $||\cdot||_{\infty,1/\psi}$ in the arguments presented in sections~\ref{sec:lubp} and ~\ref{sec:alubp} leading to Corollary~\ref{cmt1}.
\end{proof}

We now recall Lemma~$4.5$ of \cite{ALP}. \todoc{You had 4.3 here, but in the official journal version this seems to be Lemma 5 in Section 4.}
\begin{lemma}\label{restate}
Let $\psi$ be a Lyapunov function that belongs to the column span of $\Phi$ , $r \in \R^k$ be an arbitrary vector and let $r'$ be such that
\begin{align}
\Phi r'=\Phi r+||J^*-\Phi r||_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, \psi.
\end{align}
Then $r'$ is feasible for the ALP in \eqref{alp}. 
\end{lemma}
\begin{theorem}\label{mt2mn}
Let $\hv$ be the solution to the iterative scheme in \eqref{apvi} and let $\hj=\Phi \hr$ be the solution to the GRLP. Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_{\infty,1/\psi}$ be the error due to ALUB projection and let $r^*\eqdef\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_{\infty,1/\psi}$, then
\begin{align}
||\hj-\hv||_{1,c}&\leq \frac{c^\top \psi}{1-\beta_\psi}(4||J^*-\Phi r^*||_{\mn}
%\nn\\&
+||\Gamma J^*-\hg J^*||_{\mn}).
\end{align}
\end{theorem}
\begin{proof}
Let $\gamma=||J^*-\Phi r^*||_{\infty,1/\psi}$, then by choosing $r'$ as in Lemma~\ref{restate} we have
\begin{align}
||\Phi r'-J^*||_{\mn}&\leq ||\Phi r^*-J^*||_{\mn}+||\Phi r'-\Phi r^*||_{\mn}\nn\\
&=\gamma+\frac{1+\beta_\psi}{1-\beta_\psi}\gamma\nn\\
&=\frac{2}{1-\beta_\psi}\gamma.\nn
\end{align}
Since $r'$ is also feasible for the GRLP in \eqref{grlp} we have
\begin{align}
||\hj-\hv||_{1,c}&\leq||\Phi r'-\hv||_{1,c}\nn\\
&=\sum_{s\in S}c(s)\psi(s)\frac{|\Phi r'(s)-\hv(s)|}{\psi(s)}\nn\\
&\leq c^\top \psi ||\Phi r'-\hv||_{\infty,1/\psi}\nn\\
&\leq c^\top \psi (||\Phi r'-J^*||_{\infty,1/\psi}+||J^*-\hv||_{\infty,1/\psi}).
\end{align}
The result follows from Corollary~\ref{cmt1}.\\
\textbf{Main Result~$1$: Prediction Error bound in weighted $L_\infty$-norm}
\end{proof}
\begin{theorem}\label{cmt2mn}
Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2mn}, then
\begin{align}\label{finalbndmn}
||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(6 ||J^*-\Phi r^*||_{\mn}
%\nn\\&
+2||\Gamma J^*-\hg J^*||_{\mn}).
\end{align}
\end{theorem}
\begin{proof}
\begin{align}
||J^*-\hj||_{1,c}&\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn\\
&\leq c^\top \psi ||J^*-\hv||_{\mn}+||\hv-\hj||_{1,c}.\nn
\end{align}
The result now follows from Lemma~\ref{cmt1mn} and Theorem~\ref{mt2mn}.
\end{proof}

### 2015-06-13 lp.tex
eqdef and other minor fixes
Mostly streamlining the text in the alp section

%!TEX root =  autocontgrlp.tex
\section{Approximate Linear Programming}
The LP formulation in \eqref{mdplp} can be represented in short as,
\begin{align}
\begin{split}
\label{mdplpshort}
\min_{J\in \R^n}\, &c^\top J\\
\text{s.t}\mb &J\geq T J,
\end{split}
\end{align}
or 
%\text{ or }\nn\\
\begin{align}
\begin{split}
\label{shortalter}
\min_{J\in \R^n} \,&c^\top J\\
\text{s.t}\mb &EJ\geq H J,
\end{split}
\end{align}
where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp} and $E$ is an $nd\times n$ matrix given by $E=[I,\ldots,I]^\top$, i.e., $E$ is obtained by stacking $d$ identical $n\times n$ identity matrices one over the other. Note that \eqref{mdplpshort} and \eqref{shortalter} are identical programs and differ only in notation. We use notation of type \eqref{mdplpshort} whenever we prefer brevity and we use notation \eqref{shortalter} in some definitions and proof for the sake of clarity.
The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by letting $J=\Phi r$ in \eqref{mdplpshort} and is given as
\begin{align}\label{alp}
\begin{split}
\min_{r\in \R^k}\, &c^\top \Phi r\\
\text{s.t}\mb &\Phi r\geq T \Phi r.
\end{split}
\end{align}
Unless specified otherwise we use $\tr$ to denote any solution\todoc{instead of saying the solution} to the ALP and $\tj=\Phi \tr$ to denote the corresponding approximate value function. We now state the assumptions and definitions used for the rest of the paper.
\begin{assumption}\label{one}
The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \R^n$. In other words, the constant function is part of the basis.
\end{assumption}
\begin{assumption}\label{probdist}
$c=(c(i),i=1,\ldots,n)\in \R^n$ is a probability distribution, i.e., $c(i)\geq 0$ and $\sum_{i=1}^n c(i)=1$.
\end{assumption}
\begin{definition}
Given a function $\chi\colon S\ra \R^+$ we define the quantity $\beta_{\chi}$ as
\begin{align*}
\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}\,.
\end{align*}
\end{definition}
\begin{definition}
The function $\chi$ is then said to be a \emph{Lyapunov} function if $\beta_{\chi}<1$.
\end{definition}
\begin{assumption}\label{lyap}
$\psi\colon S \ra \R^+$ is a Lyapunov function and is present in the column span of the feature matrix $\Phi$.
\end{assumption}
It is straightforward to check that the function $\one$ is a Lyapunov function and trivially is present in the column span of $\Phi$. 
\begin{definition}\label{modlone}
The weighted $L_1$-norm is defined as \todoc{modified $\Rightarrow$ weighted?}
\begin{align*}
||J||_{1,c}=\sum_{s \in S} c(s)|J(s)|,
\end{align*}
where $c$ obeys Assumption~\ref{probdist}.
\end{definition}
\begin{definition}\label{modnorm}
The weighted $L_\infty$-norm is defined as follows:  \todoc{modified $\Rightarrow$ weighted? Also, the convention in math is to divide in the case of the $L_{\infty}$ norm. Not a high priority to change this, but maybe it would be good to do this in the longer term.}
\begin{align*}
||J||_{\infty,\rho}=\max_{s \in S} \frac{|J(s)|}{\rho(s)},
\end{align*}
where $\rho \colon \S \ra \R^+$ is the weighing function and $J\in \R^n$.
\end{definition}
In Definition~\ref{modnorm}, the use of the weighting function $\rho$ allows us to measure the error taking into account the relative importance of the various states. A lower value of $\rho(s)$ means that the state $s$ is less important and vice-versa.\\
We recall below Theorem~$4.2$ of \cite{ALP} which bounds the error in the approximate value function.
\begin{theorem}\label{restateval}
Let $\tr$ be the solution to the ALP in \eqref{alp}, $\tilde{J}_c=\Phi \tilde{r}_c$, $\psi$ be a Lyapunov function and $c$ be a distribution as in \eqref{probdist}, then 
\begin{align*}
||J^*-\tj||_{1,c}\leq \frac{2c^\top \psi}{1-\beta_{\psi}}\min_{r}||J^*-\Phi r||_{\mn}.
\end{align*}
\end{theorem}
We now recall Theorem~$3.1$ of \cite{ALP} that characterizes the loss in performance of the greedy policy.
\begin{theorem}\label{restatepol}
Let $\tilde{u}$ be the greedy policy with respect to the solution $\tj$ of the ALP, then 
\begin{align*}
||J^*-J_{\tu}||_{1,c}\leq \frac{1}{1-\alpha}||J^*-\tj||_{1,c'},
\end{align*}
where $c'=(1-\alpha)c^\top(I-\alpha P_{\tu})^{-1}$.
\end{theorem}
Theorems~\ref{restateval} and ~\ref{restatepol} together imply that the ALP addresses both the control and prediction problems. Please refer to \cite{ALP} for a more detailed treatment of the ALP.\\
Note that the ALP is a linear program in $k$ ($<<n$) variables as opposed to the LP in \eqref{mdplpshort} which has $n$ variables. Nevertheless, the ALP has $nd$ constraints (same as the LP) which is an issue when $n$ is large and calls for constraint approximation/reduction techniques.

>>>>

%!TEX root =  autocontgrlp.tex
\section{Approximate Linear Programming}
The LP formulation in \eqref{mdplp} can be represented in short as,
\begin{align}
\begin{split}
\label{mdplpshort}
\min_{J\in \R^n}\, &c^\top J\\
\text{s.t.}\mb &J\geq T J,
\end{split}
\end{align}
or 
%\text{ or }\nn\\
\begin{align}
\begin{split}
\label{shortalter}
\min_{J\in \R^n} \,&c^\top J\\
\text{s.t.}\mb &EJ\geq H J,
\end{split}
\end{align}
where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp} and $E$ is an $nd\times n$ matrix given by $E=[I,\ldots,I]^\top$, i.e., $E$ is obtained by stacking $d$ identical $n\times n$ identity matrices one over the other. Note that \eqref{mdplpshort} and \eqref{shortalter} are identical programs and differ only in notation. We use notation of type \eqref{mdplpshort} whenever we prefer brevity and we use notation \eqref{shortalter} in some definitions and proofs for the sake of clarity.
Recall that the vector $c\in \R^n$ must have positive entries to guarantee that the unique solution to the above LP is the optimal value function. By convention, we will also assume that $c$ is also normalized:
\begin{assumption}\label{probdist}
$c=(c(i),i=1,\ldots,n)\in \R^n$ is a positive probability distribution, i.e., $c(i)>0$ and $\sum_{i=1}^n c(i)=1$.
\todoc{I am pretty sure the positivity is needed.}
\end{assumption}

The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by adding the extra constraint $J=\Phi r$ in \eqref{mdplpshort} with $\Phi \in \R^{n\times k}$ and the new variables $r\in \R^k$. 
By substitution, this leads to
\begin{align}\label{alp}
\begin{split}
\min_{r\in \R^k}\, &c^\top \Phi r\\
\text{s.t.}\mb &\Phi r\geq T \Phi r.
\end{split}
\end{align}
Unless specified otherwise we use $\tr$ to denote any solution\todoc{instead of saying the solution} to the ALP and $\tj=\Phi \tr$ to denote the corresponding approximate value function. 
The extra constraint added that $J$ lies in the (column) span of $\Phi$ could lead to an infeasible LP. An easy way to prevent this is if the vector $\one$ whose components are all equal to one is in the span of $\Phi$.
Indeed, by \cref{shift}, for any $t\in \R$, $T (t\one ) =  \alpha t \one+T \zero \le \alpha t \one + \max_{s,a} g_a(s)$, hence $t\one \ge \alpha t \one+T\zero $ happens as soon as
$t\ge \frac{1}{1-\alpha}\max_{s,a} g_a(s)$. 
This leads to the following assumption:
\begin{assumption}\label{one}
The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \R^n$. 
In other words, the constant function is part of the basis.
\end{assumption}

We will now recall two results due to de Farias and Van Roy 
	that bound the error due to the introduction of the extra constraint in the ALP.
For this, we will need the definition of weighted $L_1$ and $L_\infty$ norms.
For any $c,\rho:S \to \R$ positive valued functions
the weighted $L_1$-norms $\norm{\cdot}_{1,c}$ 
and 
the weighted $L_\infty$-norms  $\norm{\cdot}_{\infty,\rho}$ are defined as
\begin{align*}
||J||_{1,c}=\sum_{s \in S} c(s)|J(s)|\,, \qquad
||J||_{\infty,\rho}=\max_{s \in S} \frac{|J(s)|}{\rho(s)}\,, \qquad J:S\to \R\,.
\end{align*}

We let $\R_+$ denote the set of nonnegative reals. \todoc{Move up?}
For any function $\chi\colon S\ra \R_+$, define the discounted maximal inflation of $\chi$ due to $P = (p_a)_{a\in A}$ as
\begin{align*}
\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}\,.
\end{align*}
\begin{definition}
A function $\chi:S\to\R_+$ is said to be a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ 
	if $\beta_{\chi}<1$.
\end{definition}
The error bound will be given in terms of a Lyapunov function $\psi$ for $P$ that is in the column span of $\Phi$:
\begin{assumption}\label{lyap}
$\psi\colon S \ra \R_+$ is a Lyapunov function for $P$
and is present in the column span of the feature matrix $\Phi$.
\end{assumption}
It is straightforward to check that the vector $\one$ when viewed as a $S \to \R_+$ function 
is a Lyapunov function. 
Further, by \cref{one}, $\one$ is trivially present in the column span of $\Phi$, 
hence, \cref{lyap} is not limiting.

%In Definition~\ref{modnorm}, the use of the weighting function $\rho$ allows us to measure the error taking into account the relative importance of the various states. A higher value of $\rho(s)$ means that the state $s$ is less important and vice-versa.\\
With this, we can recall the said result.  %below  which bounds the error in the approximate value function.
\begin{theorem}[Theorem~$4.2$ of \cite{ALP}]
\label{restateval}
Let $\tr$ be the solution to the ALP in \eqref{alp}, $\tilde{J}_c=\Phi \tilde{r}_c$, $\psi$ be as in \cref{lyap} 
and $c$ be a distribution as in \eqref{probdist}. Then, it holds that
\begin{align*}
||J^*-\tj||_{1,c}\leq \frac{2c^\top \psi}{1-\beta_{\psi}}\min_{r}||J^*-\Phi r||_{\mn}\,.
\end{align*}
\end{theorem}
The next result  the loss in performance of a policy that is greedy w.r.t. $J_{\tu}$:
\begin{theorem}[Theorem~$3.1$ of \cite{ALP}]
\label{restatepol}
Let $\tilde{u}$ be the greedy policy with respect to the solution $\tj$ of the ALP, then 
\begin{align*}
||J^*-J_{\tu}||_{1,c}\leq \frac{1}{1-\alpha}||J^*-\tj||_{1,c'}\,,
\end{align*}
where $c'=(1-\alpha)c^\top(I-\alpha P_{\tu})^{-1}$.
\end{theorem}
Theorems~\ref{restateval} and ~\ref{restatepol} together imply that the ALP addresses both the control and prediction problems. Please refer to \cite{ALP} for a more detailed treatment of the ALP.\\
Note that the ALP is a linear program in $k$ ($<<n$) variables as opposed to the LP in \eqref{mdplpshort} which has $n$ variables. Nevertheless, the ALP has $nd$ constraints (same as the LP) which is an issue when $n$ is large and calls for constraint approximation/reduction techniques.
\todoc{Column generation, Dantzig-Wolf decomposition?}

### 2015-06-13 mdp.tex
Mostly streamlining the text in the alp section

The basic solution methods namely value iteration, policy iteration and linear programming (LP) \cite{BertB} solve both the control and prediction problems. Of the three basic methods, in this paper, we focus on the LP formulation given by
\begin{align}\label{mdplp}
\begin{split}
\min_{J\in \R^n}\, &c^\top J\\
\text{s.t.}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \qquad s\in S, a \in A,
\end{split}
\end{align}
where $c\in \R^n_+$ is any vector whose components are all non-negative (we denote the set of non-negative reals by $\R_+$). One can show that $J^*$ is the solution to the linear program given by \eqref{mdplp} \cite{BertB}. 
Also, of the three methods, value iteration and LP formulation are value function based methods, i.e., they compute $J^*$ directly and then $u^*$ is obtained by plugging $J^*$ in \eqref{bellpol}.

>>>>

The basic solution methods namely value iteration, policy iteration and linear programming (LP) \cite{BertB} solve both the control and prediction problems. Of the three basic methods, in this paper, we focus on the LP formulation given by
\begin{align}\label{mdplp}
\begin{split}
\min_{J\in \R^n}\, &c^\top J\\
\text{s.t.}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \qquad s\in S, a \in A,
\end{split}
\end{align}
where $c\in \R^n$ is any vector whose components are all positive.
\todoc{I changed this from nonnegative to positive.} 
One can show that $J^*$ is the solution to the linear program given by \eqref{mdplp} \cite{BertB}. 
Also, of the three methods, value iteration and LP formulation are value function based methods, i.e., they compute $J^*$ directly and then $u^*$ is obtained by plugging $J^*$ in \eqref{bellpol}.
